TEMPERATURES AND METALLICITIES FOR 10,000 M DWARFS\\ IN THE \apogee\ SURVEY

### 2019-06-11 paper/draft.tex
condense size of isochrone plots

\begin{figure*}[hp!]
	\includegraphics[width=\linewidth]{figures/isochrone_cmd.png}
	\caption{Comparison of \cannon\ $\feh$ as compared to metallicity predicted by PARSEC isochrone tracks \citealt{Bressan:2012} in \gaia\ color-magnitude space. The four panels show five metallicity tracks (ranging $-0.5<$[M/H]$<0.5$) over varying ages (1, 3, 5, and 7 Gyr).}
	\label{fig:isochrone_cmd}
\end{figure*}

@@

\begin{figure*}[h]
	\includegraphics[width=\linewidth]{figures/aspcap_cannon_label_hist.png}
	\caption{Distribution of temperatures and metallicities for 10,311 sources from \thecannon\ compared to the ASPCAP pipeline. Note that \cannon\ temperatures only span $2850<T_{\rm eff}<4150$ and $-0.5<\feh<0.5$\,dex because we have imposed cutoffs for stars that fall outside of the training sample range, however for the same 10,311 stars ASPCAP predicts temperatures with slightly higher temperatures and metallicities.}
	\label{fig:aspcap_cannon_label_hist} 
\end{figure*}

@@

>>>>

@@

@@

% \begin{figure*}[hp!]
% 	\includegraphics[width=\linewidth]{figures/isochrone_cmd.png}
% 	\caption{Comparison of \cannon\ $\feh$ as compared to metallicity predicted by PARSEC isochrone tracks \citealt{Bressan:2012} in \gaia\ color-magnitude space. The four panels show five metallicity tracks (ranging $-0.5<$[M/H]$<0.5$) over varying ages (1, 3, 5, and 7 Gyr).}
% 	\label{fig:isochrone_cmd}
% \end{figure*}

\begin{figure}
	\includegraphics[width=\linewidth]{figures/cannon_vs_parsec.png}
	\includegraphics[width=\linewidth]{figures/aspcap_vs_parsec1.png}
	\caption{Comparison of \cannon\ $\feh$ as compared to metallicity predicted by PARSEC isochrone tracks \citealt{Bressan:2012} in \gaia\ color-magnitude space. The four panels show five metallicity tracks (ranging $-0.5<$[M/H]$<0.5$) over varying ages (3 and 7 Gyr).}
	\label{fig:isochrone_cmd}
\end{figure}

\begin{figure}
	\includegraphics[width=\linewidth]{figures/aspcap_vs_parsec2.png}
	\caption{}
\end{figure}

\begin{figure*}
	\plotone{figures/aspcap_cannon_label_hist.png}
	\caption{Distribution of temperatures and metallicities for 10,311 sources from \thecannon\ compared to the ASPCAP pipeline. Note that \cannon\ temperatures only span $2850<T_{\rm eff}<4150$ and $-0.5<\feh<0.5$\,dex because we have imposed cutoffs for stars that fall outside of the training sample range, however for the same 10,311 stars ASPCAP predicts temperatures with slightly higher temperatures and metallicities.}
	\label{fig:aspcap_cannon_label_hist} 
\end{figure*}
